### 2024-10-02 esop25/ipj.tex
checkpoint

In all cases, we want to determine the integrity level of computed
values based on assumed partitionins $H,C$. In the previous example,
we want to say that $\rvl{x}$ has low integrity if either client 1 or
2 is corrupt.  To this end we define \emph{security labelings}
$\seclev$ which are mappings from variables $x$ to security levels
$\latel$. By default, given a partitioning $H,C$ this labeling maps
messages to the integrity level of the owner.
\begin{definition}  
  Given $H,C$,
  define $\seclev_{H,C}$ such that for all $\mx{w}{\cid}$ we
  have $\seclev_{H,C}(\mx{w}{\cid} ) = \hilab$ if $\cid \in H$ and $\lolab$
  otherwise.
\end{definition}
During execution of a protocol, the integrity of messages and reveals
affected by values sent by other parties, as recorded in $\Delta$
obtained from its typing. We additionally need to determine
whether this impacts integrity, which we accomplish through
the inductively defined rewrite relation $\cheatj{\Delta}{H,C}{\seclev}$,
axiomatized in Figure \ref{fig-cheatj}.
Our main type safety result for integrity is then given as follows.
\begin{theorem}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$ with
  $\views(\prog) = V$, if
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and for all $H,C$ with $\cheatj{\Delta}{H,C}{\seclev}$ 
  we have $\seclev(x) = \hilab$ for all $x \in \houtputs$, then cheating
  is detectable in $\prog$.
\end{theorem}

>>>>

In all cases, we want to determine the integrity level of computed
values based on assumed partitionins $H,C$. In the previous example,
we want to say that $\rvl{x}$ has low integrity if either client 1 or
2 is corrupt.  To this end we define \emph{security labelings}
$\seclev$ which are mappings from variables $x$ to security levels
$\latel$. By default, given a partitioning $H,C$ this labeling maps
messages to the integrity level of the owner.
\begin{definition}  
  Given $H,C$,
  define $\seclev_{H,C}$ such that $\seclev_{H,C}(\mx{w}{\cid} ) = \hilab$
  if $\cid \in H$  and $\lolab$
  otherwise for all $\mx{w}{\cid}$.
\end{definition}
During execution of a protocol, the integrity of messages and reveals
affected by values sent by other parties, as recorded in $\Delta$
obtained from its typing. We additionally need to determine
whether this impacts integrity, which we accomplish through
the inductively defined rewrite relation $\cheatj{\Delta}{H,C}{\seclev}$,
axiomatized in Figure \ref{fig-cheatj}.
Our main type safety result for integrity is then given as follows.
\begin{theorem}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$ with
  $\views(\prog) = V$, if
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and for all $H,C$ with $\cheatj{\Delta}{H,C}{\seclev}$ 
  we have $\seclev(x) = \hilab$ for all $x \in \houtputs$, then cheating
  is detectable in $\prog$.
\end{theorem}

### 2024-10-02 esop25/metalang.tex
checkpoint

@@

$$
\begin{array}{rcl}
  %\notg{x} &::=& \elab{\flip{e}}{e} \mid \elab{\secret{e}}{e} \mid \elab{\mesg{e}}{e} \mid \rvl{e} \mid \out{e}\\[2mm]
  \multicolumn{3}{l}{\flab \in \mathrm{Field},\   y \in \mathrm{EVar}, \  f \in \mathrm{FName}}\\[1mm]
  %x &\in& \mathrm{EVar}\\
  %f &\in& \mathrm{FName}\\[2mm]
  e &::=& \mv \mid \flip{e} \mid \secret{e} \mid \mesg{e} \mid \rvl{e} \mid \outkw \mid e \bop e \mid
  \elet{y}{e}{e} \mid \\
  & & f(e,\ldots,e) \mid \{ \flab = e; \ldots; \flab = e \} \mid e.\flab \mid \elab{e}{e} \mid y\\
  %  & \textit{expressions}\\
  \cmd &::=& %\msend{e}{e}{e}{e} \mid \reveal{e}{e}{e} \mid \pubout{e}{e}{e} \mid
  \assign{e}{e} \mid \elab{\assert{e = e}}{e} \mid f(e,\ldots,e) \mid  \cmd;\cmd \\[2mm] %\pre{\eqs} \mid \post{\eqs} \\[1mm]
  \bop &::=& \fplus \mid \fminus \mid \ftimes \mid \concat  \\[1mm]% \textit{operators}\\[2mm]
  \mv &::=& w \mid \cid \mid \be \mid x \mid \{ \flab = \mv;\ldots;\flab = \mv \} 
  \\ % \mid \ttt{()} \\[1mm] %& \textit{values}\\[2mm]
  \mathit{fn} &::=& f(y,\ldots,y) \{ e \} \mid  f(y,\ldots,y) \{ \cmd \} %\\[1mm]%& \textit{functions}
  %\phi &::=& \elab{\flip{e}}{e} \mid \elab{\secret{e}}{e} \mid \elab{\mesg{e}}{e} \mid \rvl{e} \mid \out{e} \mid \phi \fplus \phi \mid \phi \fminus \phi \mid \phi \ftimes \phi \\
  %\eqs &::=& \phi \eop \phi \mid \eqs \wedge \eqs 
\end{array}
$$

\begin{mathpar}
  \inferrule
      {e[\mv/y] \redx \mv'}
      {\elet{y}{\mv}{e} \redx \mv'}

  \inferrule
      {\codebase(f) = y_1,\ldots,y_n,\ e \\ e_1 \redx \mv_1 \cdots e_n \redx \mv_n \\
        e[\mv_1/y_1]\cdots[\mv_n/y_n] \redx \mv}
      {f(e_1,\ldots,e_n) \redx \mv}

  \inferrule
      {e_1 \redx \mv_1 \\ \cdots \\ e_n \redx \mv_n }
      {\{ \flab_1 = e_1; \ldots; \flab_n = e_n \} \redx \{ \flab_1 = \mv_1; \ldots; \flab_n = \mv_n \} }

  \inferrule
      {e \redx \{\ldots; \flab = \mv; \ldots\}}
      {e.\flab \redx \mv}

  \inferrule
      {e_1 \redx w_1 \\ e_2 \redx w_2}
      {e_1 \concat e_2 \redx w_1w_2}

  \inferrule
      {e \redx w}
      {\mesg{e} \redx \mesg{w}}

  \inferrule
      {e_1 \redx \be_1 \\ e_2 \redx \be_2}     
      {e_1 \fplus e_2 \redx \be_1 \fplus \be_2}

  \inferrule
      {e_1 \redx \be \\ e_2 \redx \cid}
      {\elab{e_1}{e_2} \redx \elab{\be}{\cid}}
\end{mathpar}

\begin{mathpar}
  \inferrule
      {e_1 \redx x \\ e_2 \redx \elab{\be}{\cid}}
      {\assign{e_1}{e_2} \redx \xassign{x}{\be}{\cid}}

  \inferrule
      {e_1 \redx \prog_1 \\ e_2 \redx \prog_2}
      {e_1;e_2 \redx \prog_1;\prog_2}

  \inferrule
      {e_1 \redx \be_1 \\ e_2 \redx \be_2 \\ e_3 \redx \cid}
      {\elab{\assert{e_1 = e_2}}{e_3} \redx \elab{\assert{\be_1 = \be_2}}{\cid}}

  \inferrule
      {\codebase(f) = y_1,\ldots,y_n, \instr \\
        e_1 \redx \mv_1 \ \cdots \ e_n \redx \mv_n \\
        \subn = [\mv_1/y_1]\cdots[\mv_n/y_n] \\
        \subn(\instr) \redx \prog
      }
      {f(e_1,\ldots,e_n) \redx \prog}
\end{mathpar}

@@

@@

\begin{mathpar}
  \atj{x}{\varnothing}{\setit{x}}

  \inferrule
  {\atj{\phi}{R}{\ty} \\ \rx{w}{\cid}\not\in R \\ \oplus \in \setit{\fplus,\fminus}}
  {\atj{\phi \oplus \rx{w}{\cid}}{R \cup \setit{\rx{w}{\cid}}}{\setit{\cty{\rx{w}{\cid}}{\ty}}}}

  \inferrule
  {\atj{\phi_1}{R_1}{\ty_1} \\
   \atj{\phi_2}{R_2}{\ty_2} \\ \oplus \in \{ \fplus,\fminus,\ftimes \}}
  {\atj{\phi_1 \oplus \phi_2}{R_1;R_2}{\ty_1 \cup \ty_2}}
\end{mathpar}

>>>>

Practical MPC computations protocols are
typically composed of compositional units. Examples include GMW circuits
and Yao's Garbled Circuits (YGC), that are composed of so-called
garbled gates. Languages such as Fairplay \cite{269581} provide gates as
units of abstraction that are ``wired'' together by the programmer to
generate a complete circuit.

The $\fedprot$ language is low-level and does not include abstractions
for defining composable elements. So in this Section we introduce the
$\metaprot$ language that includes structured data and function
definitions for defining composable protocol elements at a higher
level of abstraction.  The $\metaprot$ language is a
\emph{metalanguage}, where $\fedprot$ protocols are the residuum of
computation. In addition to these declarative benefits of $\metaprot$,
component definitions support compositional verification of larger
protocols as we will discuss with examples in Section
\ref{section-examples}.

\metaprotsyntaxfig

@@

The syntax of $\metaprot$ is defined in Figure
\ref{fig-metaprot}.  It includes a syntax of function
definitions and records, and values $\mv$ include client ids $\cid$, identifier
strings $w$, expressions $\be$ in field $\mathbb{F}_p$, and the unit value $()$.
Expression forms allow dynamic construction of field expressions and $\minifed$ commands.
The construction of a command has the side-effect of adding to the residual
$\minifed$ protocol. Formally, we consider a complete metaprogram to include both a
codebase and a ``main'' program that uses the codebase. 
\begin{definition}
A \emph{codebase} $\codebase$ is a list of function 
declarations. We write $ \codebase(f) = y_1,\ldots,y_n,\ e$
iff $f(y_1,\ldots,y_n) \{ e \} \in \codebase$.
A \emph{metaprogram}, aka \emph{metaprotocol}  is a pair of a 
codebase and expression $\codebase, e$. We may omit
$\codebase$ if it is clear from context.  
\end{definition}

We define a small-step evaluation aka reduction relation $\redx$ in
Figure \ref{fig-metaprot}.  We write $\redxs$ to denote the
reflexive, transitive closure of $\redx$. Reduction is defined on
\emph{configurations} which are pairs of the form $\config{\prog}{e}$,
where $\prog$ is the $\minifed$ program accumulated during evaluation.
In this definition we write $e[\mv/y]$ to denote the substitution of $\mv$
for free occurrences of $y$ in $e$. The rules are mostly standard,
except when a concrete $\minifed$ assignment is encountered it is added
to the end of $\prog$.

\metaprotexprsemanticsfig

The rules rely on a definition of \emph{evaluation contexts} $E$
allowing computation within a larger program context, where $E[e]$
denotes an expression with $e$ in the hole $[]$ of $E$. The syntax
of $E$ imposes a left-to-right order of evaluation of subexpressions
for all forms.

\metaprotinstrsemanticsfig

@@

\subsubsection{$\minicat$ expression type algorithm}

\atjfig

\begin{lemma}
  If $\atj{\toeq{\phi}}{R}{\ty}$ then $\eqj{R}{\eqs}{\phi}{\ty}$ for any $\eqs$.
\end{lemma}

@@
